---
title: "Question-13"
author: "Pradeep Paladugula"
date: "6/5/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
ExamData = read.csv('Exam1Q1.csv')
adjdata = select(ExamData, Highschool, BS)
summary(adjdata)
sd(adjdata$Highschool)
mean(adjdata$Highschool)
sd(adjdata$BS)
mean(adjdata$BS)

#density plots
plot(density(adjdata$Highschool))

plot(density(adjdata$BS))

#test for normality
shapiro.test(adjdata$Highschool)
shapiro.test(adjdata$BS)

#test for skewness
agostino.test(adjdata$Highschool)
agostino.test(adjdata$BS)

# test for equality of variances/homoscedasticity/homogeneity of variance)
library(reshape2)
library(moments)
library(car)
meltData <- melt(adjdata)

leveneTest(value ~ variable, meltData)

#t-test
t.test(adjdata$Highschool, adjdata$BS, var.equal = TRUE)
tapply(meltData$value, meltData$variable, mean )
tapply(meltData$value, meltData$variable, sd )
```

    Conclusion:

    I have conducted independent t-test comparing the earnings of those with a high school diploma (M = 39.51; SD = 2.489) to those with a bachelors of science (M = 50.7666; SD = 6). I noticed significant difference between the earnings of the two groups, t(76) = -10.81217, p = 2.2e-16 < 0.05. In whoel it supports the alternative hyp[othesis that it appears the level of schooling (high school vs a BSc) has a very high impact on earnings in the firm.