---
title: "EDA Project work airbnb"
author: "Pradeep Paladugula"
date: "7/27/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, airbnb data}
library('dplyr')
library('car')

airbnbData <- read.csv('AB_NYC_2019.csv')
str(airbnbData)
newAirbnbData <- airbnbData[,c(5,9,10,11,12,15,16)]
ssAirbnbData <- subset(newAirbnbData, price > 0)


ssAirbnbData$neighbourhood_group <- factor(ssAirbnbData$neighbourhood_group)
ssAirbnbData$price <- log(ssAirbnbData$price)

model <- lm(price ~ neighbourhood_group + room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 , data = ssAirbnbData)
summary(model)
BIC(model)
AIC(model)
vif(model)

model1 <- lm(price ~ neighbourhood_group + room_type + minimum_nights + number_of_reviews + availability_365 , data = ssAirbnbData)
summary(model1)
BIC(model1)
AIC(model1)
vif(model1)

model2 <- lm(price ~ neighbourhood_group + room_type + minimum_nights + number_of_reviews, data = ssAirbnbData)
summary(model2)

model3 <- lm(price ~ neighbourhood_group + room_type + minimum_nights + availability_365, data = ssAirbnbData)
summary(model3)

model4 <- lm(price ~ neighbourhood_group + room_type + number_of_reviews + availability_365, data = ssAirbnbData)
summary(model4)

model5 <- lm(price ~ neighbourhood_group + room_type + minimum_nights, data = ssAirbnbData)
summary(model5)

model6 <- lm(price ~ neighbourhood_group + room_type + availability_365, data = ssAirbnbData)
summary(model6)

anova(model1, model3)
cutoff <- 4/((nrow(ssAirbnbData)-length(model1$residuals)-1))

library('base')
cooksd <- cooks.distance(model1)

influential <- as.numeric(names(cooksd)[(cooksd > (4/nrow(ssAirbnbData)))])

# Alternatively, you can try to remove the top x outliers to have a look
# top_x_outlier <- 2
# influential <- as.numeric(names(sort(cooksd, decreasing = TRUE)[1:top_x_outlier]))

airbnbNoOutliers <- ssAirbnbData[-influential, ]
str(airbnbNoOutliers)

model1_new <- lm(price ~ neighbourhood_group + room_type + minimum_nights + number_of_reviews + availability_365 , data = airbnbNoOutliers)
summary(model1_new)
BIC(model1_new)
AIC(model1_new)
vif(model1_new)

predicted_values <- model1_new$fitted.values
airbnbNoOutliers$predicted_values <- predicted_values

head(airbnbNoOutliers)

qqplot(predicted_values, model1_new$residuals)
qqline(predicted_values, model1_new$residuals)
```

Technical Approch:

Data cleaning (total observations reduced from 48895 to 46915). Used logarithmic regression to reduced the skewness in the data

Used multiple regression model to prove the conclusion. Applied linear regression model on the specifically chosen columns from the data. Considered price (dependent variable) and neighbourhood_group, room_type, minimum_nights, number_of_reviews, availability_365 (Independent variable/predictors). Calculated_host_listings_count was not consider as it was statistically insignificant. 

Used cook's distance to find the outliers. And upon removed the outliers from the in the data

Using ANOVA method choose the best model. And conduct experiment to find out how models behaved before and after  removal of outliers.

Finally explained various factors why the variance in price of listing can be explained by 5 predictors mentioned above.



Conclusion:

A Linear regression model was conducted to predict price variations, based on the neighbourhood_group, room_type, minimum_nights, number_of_reviews, availability_365 observations. All the regression assumptions were met. A significant regression equation was found (F(10,48873)=4385, p-value < 0.001, R^2 value = 0.4729, BIC = 72432, AIC = 72326). The best fit model was analysed without calculated_host_listings_count and before and after outliers were removed. Model1 before outliers were removed (F(10,48873)=4385, p-value < 0.001, R^2 value = 0.4729, BIC = 72422, AIC = 72325). Model1 after Outliers removed (F(10,46905)=5359, p-value < 0.001, R^2 value = 0.507, BIC = 62866, AIC = 62770). When compared the output of Model1 before and after outliers removed, the results suggested that the 50% of variance in price of listing can be explained by 5 predictors namely neighbourhood_group, room_type, minimum_nights, number_of_reviews, availability_365.

