---
title: "mid-term-q21"
author: "Pradeep Paladugula"
date: "2/23/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, mtcars data}
library('ggplot2')
library('e1071')
library('datasets')
data(mtcars)
mtcars
head(mtcars)
```


    The Null Hypothesis is the number of miles per gallon of the cars does not depend on the number of cylinders, hors power and gear(transmission type)
    
    The Alternative Hypotheses is the number of miles per gallon of the cars has the direct correlation with the number of cylinders used, the vehiclehorse power and gear(transmission type)
    
    Dependant Variable: Miles per Gallon
    Independent Variables: Cylinders, Horse Power, Type of Gear
    
    Apart from the dependant and Independant variables, the rest of the data is not considered in this research work. 
    
    From looking the data, I noticed any missing data, NA's and error is the data. the data seems to be pretty good.
    
```{r, Mileage of automatic transmission cars}
mtcars$am = factor(mtcars$am, levels = c(0,1), labels = c("automatic", "manual"))

hist(mtcars[mtcars$am == "automatic",]$mpg, main = "Mileage of automatic transmission cars", xlab = "Miles", ylab = "Frequency")
```

```{r, Mileage of manual transmission cars}
hist(mtcars[mtcars$am == "manual",]$mpg, main = "Mileage of automatic transmission cars", xlab = "Miles", ylab = "Frequency")
```

```{r, summary of manual and automatic transmission cars}
summary(mtcars[mtcars$am == "automatic",]$mpg)

summary(mtcars[mtcars$am == "manual",]$mpg)
```

```{r}
ggplot(mtcars, aes(hp, mpg)) + geom_point()+geom_smooth(method = "lm", se = FALSE) + ggtitle("Relation between mpg and HP") + xlab("hp") + ylab("mpg")
```

```{r}
ggplot(mtcars, aes(am, mpg)) + geom_point()+geom_smooth(method = "lm", se = FALSE) + ggtitle("Relation between mpg and transmission type") + xlab("am") + ylab("mpg")
```

```{r}

ggplot(mtcars, aes(cyl, mpg)) + geom_point()+geom_smooth(method = "lm", se = FALSE) + ggtitle("Relation between mpg and cyl") + xlab("cyl") + ylab("mpg")
```
    
    