---
title: "Regression, Mediation, Moderation"
author: "Pradeep Paladugula"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Title*: The influence of cognitive and affective based job satisfaction measures on the relationship between satisfaction and organizational citizenship behavior

*Abstract*: One of the most widely believed maxims of management is that a happy worker is a productive worker. However, most research on the nature of the relationship between job satisfaction and job performance has not yielded convincing evidence that such a relationship exists to the degree most managers believe. One reason for this might lie in the way in which job performance is measured. Numerous studies have been published that showed that using Organizational Citizenship Behavior to supplant more traditional measures of job performance has resulted in a more robust relationship between job satisfaction and job performance. Yet, recent work has suggested that the relationship between job satisfaction and citizenship may be more complex than originally reported. This study investigated whether the relationship between job satisfaction and citizenship could depend upon the nature of the job satisfaction measure used. Specifically, it was hypothesized that job satisfaction measures which reflect a cognitive basis would be more strongly related to OCB than measures of job satisfaction, which reflect an affective basis. Results from data collected in two midwestern companies show support for the relative importance of cognition based satisfaction over affect based satisfaction. Implications for research on the causes of citizenship are discussed.

# Dataset:
    
    - Dependent variable (Y): OCB - Organizational citizenship behavior measure
    -	Independent variables (X)
        - Affective - job satisfaction measures that measure emotion
        - Cognitive - job satisfaction measures that measure cognitions (thinking)
        -	Years - years on the job
        -	Type_work - type of employee measured (secretary, assistant, manager, boss)	

# Data Screening:

Assume the data is accurate with no missing values.  You will want to screen the dataset using all the predictor variables to predict the outcome in a simultaneous multiple regression (all the variables at once).  This analysis will let you screen for outliers and assumptions across all subsequent analyses/steps. Be sure to factor type_work.

```{r starting}
library('foreign')
data <- read.spss('08_data.sav', to.data.frame=TRUE)
data
summary(data)
```
```{r}
str(data)
```

## Outliers
    
    a.	Leverage:
        i.	What is your leverage cut off score? 0.0875
        ii.	How many leverage outliers did you have? 7

```{r leverage}
screen = lm(OCB ~ cognitive + affective + years + type_work, data = data)
summary(screen)
```
```{r}
k = 4
leverage = hatvalues(screen) 
cutlev = (2*k+2)/nrow(data) 
cutlev
badlev = leverage > cutlev
badlev
table(badlev)
```
        
    b.	Cook's:
        i.	What is your Cook's cut off score? 0.02614379
        ii.	How many Cook's outliers did you have? 9
        
```{r cooks}
cooks = cooks.distance(screen) 
cooks
cutcooks = 4 / (nrow(data) - k - 1) 
cutcooks
badcooks = cooks > cutcooks 
table(badcooks)
```
        
    c.	Mahalanobis:
        i.	What is your Mahalanobis df? OCB, cognitive, affective, years
        ii.	What is your Mahalanobis cut off score? 18.46683
        iii.	How many outliers did you have for Mahalanobis? None
        
```{r mahal}
mahal <- mahalanobis(data[ , -1], 
                    colMeans(data[ , -1]),
                    cov(data[ , -1])) 
cutmahal = qchisq(1-.001, ncol(data[ , -5])) 
cutmahal
badmahal = mahal > cutmahal 
table(badmahal)
```
        
    d.	Overall:
        i.	How many total outliers did you have across all variables? None
        ii.	Delete them!

```{r overall}
totalout = badlev + badcooks + badmahal
table(totalout)
```

# Assumptions:

## Additivity:

    a.	Include a correlation table of your independent variables.
    b.	Do your correlations meet the assumption for additivity (i.e. do you have multicollinearity)?
    Yes the additivity has met and have the evidence of multicolinearity.

```{r additivity}
noout = subset(data, totalout < 2)
screen1 = lm(OCB ~ cognitive + affective + years + type_work, data = noout) 
standardized = rstudent(screen1) 
fitted = scale(screen1$fitted.values)
summary(screen1, correlation = T)
```

## Linearity: 

    a.	Include a picture that shows how you might assess multivariate linearity.
    b.	Do you think you've met the assumption for linearity? 
        By looking at graph it looks like it amlost linear.

```{r linearity}
qqnorm(standardized) 
abline(0,1)
```

## Normality: 

    a.	Include a picture that shows how you might assess multivariate normality.
    b.	Do you think you've met the assumption for normality? Yes, almost looking similar

```{r normality}
hist(standardized)
```

## Homogeneity and Homoscedasticity: 

    a.	Include a picture that shows how you might assess multivariate homogeneity.
    b.	Do you think you've met the assumption for homogeneity?
        No homogeneity is not met
    c.	Do you think you've met the assumption for homoscedasticity?
        Yes the assumption for homoscedasticity is met.\, the value lies between -4 to 4.
    
```{r homogs}
plot(fitted, standardized) 
abline(0,0, v = 0) 
```

# Hierarchical Regression:

    a.	First, control for years on the job in the first step of the regression analysis.
    b.	Then use the factor coded type of job variable to determine if it has an effect on organizational citizenship behavior.
    c.	Last, test if cognitive and affect measures of job satisfaction are predictors of organizational citizenship behavior. 
    d.  Include the summaries of each step, along with the ANOVA of the change between each step.
    
```{r hierarchical}
step1 = lm(OCB ~ years, data = noout)
step2 = lm(OCB ~ years + type_work, data = noout) 
step3 = lm(OCB ~ years + type_work + cognitive + affective, data = noout)
summary(step1)
summary(step2)
summary(step3)
anova(step1, step2, step3)
```

# Mediation

    a.  Calculate a mediation model wherein the number of years mediates the relationship between affective measurements and OCB.
    b.  Include each path and summaries of those models.
    c.  Include the Sobel test.
    d.  Include the bootstrapped indirect effect. 

```{r mediation}
model1 = lm(OCB ~ affective, data = data) 
summary(model1)
model2 = lm(years ~ affective, data = data) 
summary(model2)
model3 = lm(OCB ~ affective + years, data = data) 
summary(model3)
a = coef(model2)[2] 
b = coef(model3)[3] 
SEa = summary(model2)$coefficients[2,2]
SEb=summary(model3)$coefficients[3,2] 
zscore = (a * b)/(sqrt((b^2 * SEa^2)+(a^2 * SEb^2)+(SEa * SEb))) 
zscore
pnorm(abs(zscore), lower.tail = F)*2
total = coef(model1)[2] 
direct = coef(model3)[2] 
indirect = a*b
total; direct; indirect
indirectsaved = function(formula2, formula3, dataset, random) 
  { d = dataset[random, ] #randomize by row 
model2 = lm(formula2, data = d) 
model3 = lm(formula3, data = d) 
a = coef(model2)[2] 
b = coef(model3)[3] 
indirect = a*b 
return(indirect) }
library(boot)
bootresults = boot(data = data, statistic = indirectsaved, formula2 = years ~ affective, formula3 = OCB ~ affective + years, R = 1000)
bootresults
boot.ci(bootresults, conf = .95, type = "norm")
```

# Write up:
    
    Hierarchical regression only!
    a.	Include a brief description of the experiment, variables, and order entered into steps.
    b.	Include a brief section on the data screening/assumptions.
    c.	Include the all F-values for each step of the model - you can reference the above table.
      Step 1
      Residual standard error: 9.82 on 157 degrees of freedom
      Multiple R-squared:  0.0004731,	Adjusted R-squared:  -0.005893 
      Step2
      Residual standard error: 4.208 on 154 degrees of freedom
      Multiple R-squared:  0.8199,	Adjusted R-squared:  0.8153
      Setp3
      Residual standard error: 3.753 on 152 degrees of freedom
      Multiple R-squared:  0.8587,	Adjusted R-squared:  0.8531
      
      
    d.	Include all the b or beta values for variables in the step they were entered.  So, you will not have double b values for any predictor - you can reference the above table.
    
    years               0.14038     
    type_workassistant 11.34102
    type_workmanager   15.95303
    type_workboss      21.57443
    cognitive           0.02905  
    affective           0.06148
    
    e.	Include an interpretation of the results (dummy coding, do our results match the study results, etc.).
    
Answers for a adn b:

In step 1, Number of Years on the job was used to control previous experience. Here the model wasn’t significant and so this variable wasn’t a correct predictor of OCB. in the step 2, Type of Employee was entered as dummy variable sing secretary as a comparison group. From the models I saw that there was a significant increase in prediction confidence. Bosses, Assistants and Managers had significantly high OCBs than secretaries. In the step 3, I have added cognitive and affect measures of job satisfaction to test if they are predictors of OCB. While the addition was significant, cognition satisfaction was not a significant predictor, while affective satisfaction was positively correlated with OCB



